A statistical analysis of a counterstrike game: Boston 2018

### 2021-01-27 inst/counterstrike.Rmd
consistentification

```{r, useit}
H <- hyper2(pnames=c(team1,team2))
for(i in zacslist){
  H <- H + counterstrike_maker(team1,team2, deathorder=i)
}
```

@@

```{r, plotit}
dotchart(maxp(H),pch=16,main='observed data')
```

@@

datapoint <- loglik(indep(maxp(H)),H) - loglik(indep(equalp(H)),H)

n <- 100  # takes about 5 minutes for n=1000 trials
distrib <- rep(0,n)
for(i in seq_len(n)){
  Hrand <- hyper2(pnames=c(team1,team2))
  for(jj in 1:6){
    pp <- rdeath(team1,team2)
    Hrand <- Hrand + counterstrike_maker(team1,team2, pp)
	}
  distrib[i] <- loglik(indep(maxp(Hrand)),Hrand) - loglik(indep(equalp(H)),Hrand)
}

@@

>>>>

```{r, useit}
counterstrike <- hyper2(pnames=c(team1,team2))
for(i in zacslist){
  counterstrike <- counterstrike + (counterstrike_maker(team1,team2, deathorder=i))
}
```

@@

```{r, plotit}
counterstrike_maxp <- maxp(counterstrike)
dotchart(counterstrike_maxp,pch=16,main='observed data')
```

@@

datapoint <- loglik(indep(maxp(counterstrike)),counterstrike) - loglik(indep(equalp(counterstrike)),counterstrike)

n <- 100  # takes about 5 minutes for n=1000 trials
distrib <- rep(0,n)
for(i in seq_len(n)){
  Hrand <- hyper2(pnames=c(team1,team2))
  for(jj in 1:6){
    pp <- rdeath(team1,team2)
    Hrand <- Hrand + counterstrike_maker(team1,team2, pp)
	}
  distrib[i] <- loglik(indep(maxp(Hrand)),Hrand) - loglik(indep(equalp(counterstrike)),Hrand)
}

@@

### Package dataset

Following lines create `counterstrike.rda`, residing in the `data/` directory of the package.

```{r,label=savecounterstrikedataset}
save(counterstrike,counterstrike_maxp,zacslist,file="counterstrike.rda")
```
